\chapter{Testing}\label{testing}
The previous chapter described the implementation process of the prototype VR application. In this chapter, it is examined, whether the application fulfils the requirement of helping prospective students in choosing their profession by visualizing IT job roles. As outlined in the introduction, this is the main objective of the project. In general, it is difficult to find an objective method to prove or disapprove this hypothesis. This is because VR creates an unique user experience which is subjective and varies with every user. In this project, several test persons played the VR application and answered questions about their subjective experience. This chapter will explain the testing procedure and present the results of the tests.
\section{Test design}
At the beginning of the testing process, the software engineer scene was completed. The world scene contained the introduction to the game and the entrance point to the software engineer scene. The focus of the testing outcome was therefore, how the idea of the software engineer job role has changed for the test persons through playing the VR application. In order to create measurable data, the test is designed as followed:

\paragraph{Before playing prototype} At the beginning, participants answer some basic questions about their age, gender, which school they are and their pre experience in VR. After this they are asked four questions about their subjective understanding of the software engineer job role. Than they get a short introduction on how to use the controller in the game and the VR headset is fitted for them, so that they feel comfortable. 
\paragraph{Playing prototype} Participants get a short introduction on how to use the controller and than they are told to explore the virtual environment and solve tasks in their game on their own. However they are allowed to ask questions if they stuck in the game or feel disorientated. The participants play one full walkthrough of the prototype which includes exploration of the world scene, clicking on the interactive building and entering the software engineering laboratory. In the software engineer scene they find the desk and solve the mini game. After they solved the mini game correctly they can watch the drone animation and then they are told to exit the game and put off the VR headset by the virtual assistant.
\paragraph{After playing prototype}
\section{Testing group}
\section{Questionnaire}
\section{Testing environment}
\section{Results}